A Prediction of the 2024 U.S. Election Outcome 

### 2024-11-04 paper/paper.qmd
renew intro

---
title: "A Prediction of the 2024 U.S. Election"
subtitle: "Prediction Based on MRP Analysis of Harris Lost"
author: 
  - Shanjie Jiao
  - Aman Rana
  - Kevin Shen
thanks: "Code and data are available at: [https://github.com/Jie-jiao05/2024_US_Election.git)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

In this paper, multiple linear regression will be used to fit the dataset provide by Five Thirty Eight[use citation] to estimate Trump's election rate.

## Results paragraph

@@

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data we will discuss the MLR used in the prediction and the result of the MLR with its predictor variables and the response after transformation. @sec-dis the shortcomings of the study and areas for improvement will be described. @sec-A A Deep Dive to a pollster will be conducted, and @sec-B We will given a idealized survey and methodology

@@

# Appendix 
## A: Emerson College Polling Methodology Analysis

@@

## B: Idealized Survey Methodology – $100K Budget

>>>>

---
title: "A Prediction of the 2024 U.S. Election Outcome "
subtitle: "A Bayesian Spline Regression Analysis of Kamala Harris's Winning"
author: 
  - Shanjie Jiao
  - Aman Rana
  - Kevin Shen
thanks: "Code and data are available at: [https://github.com/Jie-jiao05/2024_US_Election.git)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

The estimand of this study is the predicted outcome of the 2024 U.S. Presidential Election for either Donald Trump or Kamala Harris, based on aggregated polling averages. Our analysis employs Bayesian spline regression to effectively capture the dynamic changes in voting trends over time, allowing us to forecast the likely election result. By comparing the predicted probabilities for both candidates, we aim to identify the probable winner based on current trends in voter support.

## Results paragraph
Using Bayesian spline regression analysis on the dataset provided by FiveThirtyEight [@FiveThirtyEight], this study forecasts the outcome of the 2024 U.S. election, predicting a victory for Kamala Harris.

@@

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data we will discuss the MLR used in the prediction and the result of the MLR with its predictor variables and the response after transformation. @sec-dis the shortcomings of the study and areas for improvement will be described. @sec-Appendix-A A Deep Dive to a pollster will be conducted, and @sec-Appendix-B We will given a idealized survey and methodology

@@

# Appendix 
## A: Emerson College Polling Methodology Analysis {#sec-Appendix-A}

@@

## B: Idealized Survey Methodology – $100K Budget {#sec-Appendix-B}
